### 2013-11-12 Rcode/conservativepm.Rmd
update ggplot2 figures

```{r}
basicsim=function(mixsd,mixpi_alt,seedval = 100,nsamp=1000,niter=50){
  require(ashr)
  require(qvalue)
  require(fdrtool)
  require(mixfdr)
  require(locfdr)
  set.seed(seedval)  
  beta =list()
  betahatsd=list()
  betahat = list()
  zscore = list()
  pval = list()
  betahat.ash.n = list()
  betahat.ash.u = list()
  betahat.ash.npm = list()
  betahat.qval = list()
  betahat.fdrtool = list()
  betahat.locfdr = list()
  betahat.mixfdr = list()
  pi0 = rep(0,niter)
  for(i in 1:niter){
    pi0[i]=runif(1,0,1)
    mixpi = c(pi0[i],(1-pi0[i])*mixpi_alt)
    sd = sample(mixsd,nsamp,prob=mixpi,replace=TRUE )
    beta[[i]] = rnorm(nsamp,0,sd)
    betahatsd[[i]] = 1
    betahat[[i]] = beta[[i]]+rnorm(nsamp,0,betahatsd[[i]])
    zscore[[i]] = betahat[[i]]/betahatsd[[i]]
    pval[[i]] = pchisq(zscore[[i]]^2,df=1,lower.tail=F)
    betahat.ash.n[[i]] = ash(betahat[[i]],betahatsd[[i]],pointmass=TRUE,prior="nullbiased",gridmult=2)
    betahat.ash.u[[i]] = ash(betahat[[i]],betahatsd[[i]],pointmass=TRUE,prior="uniform",gridmult=2)
    betahat.ash.npm[[i]] = ash(betahat[[i]],betahatsd[[i]],pointmass=FALSE,prior="uniform",gridmult=2)
    betahat.qval[[i]] = qvalue(pval[[i]])
    betahat.fdrtool[[i]] = fdrtool(pval[[i]],statistic="pvalue",plot=FALSE)
    betahat.locfdr[[i]] = locfdr(zscore[[i]],nulltype=0,plot=0)
    betahat.mixfdr[[i]] = mixFdr(zscore[[i]],noiseSD=1,theonull=TRUE,plot=FALSE)
  }
  return(list(beta =beta,
  betahatsd=betahatsd,
  betahat = betahat,
  zscore = zscore,
  pval = pval,
  betahat.ash.n = betahat.ash.n,
  betahat.ash.u = betahat.ash.u,
  betahat.ash.npm = betahat.ash.npm,
  betahat.qval = betahat.qval,
  betahat.fdrtool = betahat.fdrtool,
  betahat.locfdr = betahat.locfdr,
  betahat.mixfdr = betahat.mixfdr,
    pi0=pi0))
}    
mixsd = c(0,0.25,0.5,1,2)
mixpi_alt = c(0.4,0.2,0.2,0.2) #mixture proportions under the alternative
simres1 = basicsim(mixsd,mixpi_alt)
simres2= basicsim(c(0,4),c(1))
```

Show illustrative example
```{r}
plot_FDR_hist=function(sim,iter=1){
  hh.pval = sim$pval[[iter]]
  hh.zscore = sim$zscore[[iter]]
  altcol="cyan" #colors to use
  nullcol="blue" 
  nc=40 #number of bins in histograms
  ncz = 100 # number of bins in z score histograms

  hh.hist =hist(hh.pval,freq=FALSE,xlab="p value",main="Distribution of p values",nclass=nc,col=altcol)

@@

```{r}
#  par(mfcol=c(3,3))
  plot_ecdf=function(sims){
    for(i in 1:length(sims$beta)){
       plot(ecdf(sims$beta[[i]]),xlim=c(-6,6),main=paste0("iteration ",i))
       x = seq(-6,6,length=1000)
       lines(cdf.ash(sims$betahat.ash.n[[i]],x),col=2,lwd=2)
       lines(cdf.ash(sims$betahat.ash.u[[i]],x),col=3,lwd=2)
    }
  }
  plot_ecdf(simres1)
  plot_ecdf(simres2)
```

@@

@@

```{r}
  plot(betahat.ash.n[[1]]$lfdr,betahat.ash.u[[1]]$lfdr,xlab="null-biased prior",ylab="uniform prior", main="fdr is not robust to estimated pi0",xlim=c(0,0.2),ylim=c(0,0.2))
  abline(a=0,b=1,col=2,lwd=2)
```

```{r}
  plot(betahat.ash.n[[1]]$lfsr,betahat.ash.u[[1]]$lfsr,xlab="null-biased prior",ylab="uniform prior", main="fsr is more robust to estimated pi0",xlim=c(0,0.2),ylim=c(0,0.2))
  points(betahat.ash.n[[1]]$lfsr,betahat.ash.npm[[1]]$lfsr,col=3)
  abline(a=0,b=1,col=2,lwd=2)
```

```{r}
  plot(betahat.ash.n[[1]]$lfsra,betahat.ash.u[[1]]$lfsra,xlab="null-biased prior",ylab="uniform prior", main="fsra is still more robust to estimated pi0",xlim=c(0,0.2),ylim=c(0,0.2))
  points(betahat.ash.n[[1]]$lfsra,betahat.ash.npm[[1]]$lfsra,col=3)
  abline(a=0,b=1,col=2,lwd=2)
```

```{r}
  plot(betahat.ash.n[[1]]$lfsr,2*betahat.ash.npm[[1]]$lfsr,xlab="null-biased prior",ylab="uniform prior", main="fsra is still more robust to estimated pi0",xlim=c(0,0.2),ylim=c(0,0.2))
  points(betahat.ash.n[[1]]$lfsra,betahat.ash.npm[[1]]$lfsra,col=3)
  abline(a=0,b=1,col=2,lwd=2)
```

@@

```{r}
  hist(pval[[1]])
```

```{r}
hh.ashtrue = hh.ashz
hh.ashtrue$fitted.g$pi = c(2/3,1/15,1/15,1/15,1/15,1/15)
hh.ashtrue$fitted.g$mean = c(0,0,0,0,0,0)
hh.ashtrue$fitted.g$sd = sqrt(c(0,1,0.2,0.4,0.8,3))

loglik(hh.ashtrue,betahat,sebetahat)
loglik(hh.ashz,betahat,sebetahat)
```

>>>>

```{r}
opts_knit$set(progress = TRUE, verbose = TRUE,root.dir="~/Documents/git/ash/paper/Rcode")
require(ashr)
require(qvalue)
require(fdrtool)
require(mixfdr)
require(locfdr)
require(ggplot2)
#bsd gives standard deviation of beta
#pi0 is simulated to be uniform on [minpi0,1]
basicsim=function(mixsd,mixpi_alt,bsd=1,minpi0=0,seedval = 100,nsamp=1000,niter=50){  
  set.seed(seedval)  
  beta =list()
  betahatsd=list()
  betahat = list()
  zscore = list()
  pval = list()
  betahat.ash.n = list()
  betahat.ash.u = list()
  betahat.ash.npm = list()
  betahat.ash.true = list()
  betahat.qval = list()
  betahat.fdrtool = list()
  betahat.locfdr = list()
  betahat.mixfdr = list()
  pi0 = rep(0,niter)
  for(i in 1:niter){
    pi0[i]=runif(1,minpi0,1)
    mixpi = c(pi0[i],(1-pi0[i])*mixpi_alt)
    sd = sample(mixsd,nsamp,prob=mixpi,replace=TRUE )
    beta[[i]] = rnorm(nsamp,0,sd)
    betahatsd[[i]] = bsd
    betahat[[i]] = beta[[i]]+rnorm(nsamp,0,betahatsd[[i]])
    zscore[[i]] = betahat[[i]]/betahatsd[[i]]
    pval[[i]] = pchisq(zscore[[i]]^2,df=1,lower.tail=F)
    betahat.ash.n[[i]] = ash(betahat[[i]],betahatsd[[i]],pointmass=TRUE,prior="nullbiased",gridmult=2)
    betahat.ash.u[[i]] = ash(betahat[[i]],betahatsd[[i]],pointmass=TRUE,prior="uniform",gridmult=2)
    betahat.ash.npm[[i]] = ash(betahat[[i]],betahatsd[[i]],pointmass=FALSE,prior="uniform",gridmult=2)
    betahat.ash.true[[i]] = ash(betahat[[i]],betahatsd[[i]],g=normalmix(mixpi,rep(0,length(mixpi)),mixsd))

    betahat.qval[[i]] = qvalue(pval[[i]])
    betahat.fdrtool[[i]] = fdrtool(pval[[i]],statistic="pvalue",plot=FALSE)
    betahat.locfdr[[i]] = locfdr(zscore[[i]],nulltype=0,plot=0)
    betahat.mixfdr[[i]] = mixFdr(zscore[[i]],noiseSD=1,theonull=TRUE,plot=FALSE)
  }
  return(list(beta =beta,
  betahatsd=betahatsd,
  betahat = betahat,
  zscore = zscore,
  pval = pval,
  betahat.ash.n = betahat.ash.n,
  betahat.ash.u = betahat.ash.u,
  betahat.ash.npm = betahat.ash.npm,
  betahat.ash.true=betahat.ash.true,
  betahat.qval = betahat.qval,
  betahat.fdrtool = betahat.fdrtool,
  betahat.locfdr = betahat.locfdr,
  betahat.mixfdr = betahat.mixfdr,
    pi0=pi0))
}    
```

```{r, cache=TRUE}
mixsd = c(0,0.25,0.5,1,2)
mixpi_alt = c(0.4,0.2,0.2,0.2) #mixture proportions under the alternative

simres1 = basicsim(mixsd,mixpi_alt,niter=200,nsamp=1000)
simres1a = basicsim(mixsd,mixpi_alt,niter=200,nsamp=10000)
simres2= basicsim(c(0,4),c(1))
simres3=basicsim(c(0,4),c(1),bsd=c(rep(1,500),rep(10,500)))
simres4=basicsim(c(0,4),c(1),bsd=c(rep(1,500),rep(10,500)),minpi0=0.9,seed=200)
```

Show illustrative example
```{r}
altcol="cyan" #colors to use
nullcol="blue" 
nc=40 #number of bins in histograms
ncz = 100 # number of bins in z score histograms

plot_FDR_hist=function(sim,iter=1){
  hh.pval = sim$pval[[iter]]
  hh.zscore = sim$zscore[[iter]]
  hh.hist =hist(hh.pval,freq=FALSE,xlab="p value",main="Distribution of p values",nclass=nc,col=altcol)

@@

```{r}
#  par(mfcol=c(3,3))
  plot_ecdf=function(sims){
    for(i in 1:length(sims$beta)){
       plot(ecdf(sims$beta[[i]]),xlim=c(-6,6),main=paste0("iteration ",i))
       x = seq(-6,6,length=1000)
       lines(cdf.ash(sims$betahat.ash.n[[i]],x),col=2,lwd=2)
       lines(cdf.ash(sims$betahat.ash.u[[i]],x),col=3,lwd=2)
       lines(cdf.ash(sims$betahat.ash.true[[i]],x),col=4,lwd=2)
    }
  }
  plot_ecdf(simres1)
  plot_ecdf(simres2)
```

@@

  plot_pi1 = function(sims){
    pi0=sims$pi0  
    pi0_ash.n=unlist(lapply(sims$betahat.ash.n,get_pi0))
    pi0_ash.u=unlist(lapply(sims$betahat.ash.u,get_pi0)) 
    pi0_fdrtool = unlist(lapply(sims$betahat.fdrtool,get_pi0.fdrtool))
    pi0_locfdr=unlist(lapply(sims$betahat.locfdr,get_pi0.locfdr))
    pi0_mixfdr = unlist(lapply(sims$betahat.mixfdr,get_pi0.mixfdr))
    pi0_qval = unlist(lapply(sims$betahat.qval,"[[","pi0"))

    res = data.frame(pi0=pi0,qvalue=pi0_qval,mixfdr=pi0_mixfdr, locfdr=pi0_locfdr, fdrtool=pi0_fdrtool,ash.nullbiased=pi0_ash.n,ash.uniform=pi0_ash.u)
    require(reshape2)
    res.melt = melt(res, id.vars=c("pi0"),variable.name="Method")
    p=ggplot(data=res.melt,aes(1-pi0,log2((1-value)/(1-pi0)),colour=Method)) +geom_point(shape=16) +
#        geom_abline(colour = "black") +
        xlab("True pi1") +
        ylab("log2(Estimated pi1/True pi1)")
    print(p +scale_y_continuous(limits=c(-4,4)) +
          scale_x_continuous(limits=c(0,1)))

@@

```{r}
mean_quant=function (x, mult = 1){
      x <- na.omit(x)
      sd <- mult * sqrt(var(x))
      mean <- mean(x)
      data.frame(y = median(x), ymin = quantile(x,0.25) , ymax = quantile(x,0.75))
}

#ptype indicates what type of plot to do
#maxlfsr controls maximum x axis value
#maxy controls maximum y axis value
  plot_lfsr=function(sims,maxlfsr=0.1,ptype=c("lfsr","lfsra","lfdr"),maxy=1){
    ptype=match.arg(ptype)
    xlabtype = ifelse(ptype=="lfdr","lfdr","lfsr")
    res=list()
    for(i in 1:length(sims)){
      lfsr.ash.n= unlist(lapply(sims[[i]]$betahat.ash.n,"[[",ptype))
      lfsr.ash.u= unlist(lapply(sims[[i]]$betahat.ash.u,"[[",ptype))
      if(ptype=="lfdr"){
        lfsr.ash.true= unlist(lapply(sims[[i]]$betahat.ash.true,"[[","lfdr"))
        lfdr.mixfdr = unlist(lapply(sims[[i]]$betahat.mixfdr,"[[","fdr"))
        lfdr.locfdr = unlist(lapply(sims[[i]]$betahat.locfdr,"[[","fdr"))
      } else {
         lfsr.ash.true= unlist(lapply(sims[[i]]$betahat.ash.true,"[[","lfsr"))
      }

      subset = lfsr.ash.true<maxlfsr

      if(length(subset)>0){  
        res[[i]] = data.frame(Scenario=i,ash.nullbiased=lfsr.ash.n[subset],
                      ash.uniform=lfsr.ash.u[subset],
                      Bayes=0.1*maxlfsr*findInterval(lfsr.ash.true[subset],seq(0,maxlfsr,length=11))-0.05*maxlfsr)
        if(ptype=="lfdr"){
          res[[i]]=data.frame(res[[i]],mixfdr = lfdr.mixfdr[subset])
        }
      }
    }

    require(reshape2)

    res.melt = melt(res, id.vars=c("Bayes","Scenario"),variable.name="Method")

    cbbPalette <- c("#000000","#E69F00", "#56B4E9", "#009E73", "#F0E442", "#0072B2", "#D55E00", "#CC79A7")
    labels = c('ash (null-biased)','ash (uniform)')
    breaks = c("ash.nullbiased","ash.uniform")
    if(ptype=="lfdr"){
      labels = c('mixfdr', labels)
      breaks = c("mixfdr", breaks)
    }

    p=ggplot(data=res.melt,aes(Bayes,value,colour=Method)) + 
        facet_grid(. ~ Scenario) +
        #scale_fill_manual(values=cbbPalette) +
        #scale_colour_manual(values=cbbPalette) +
        geom_point(size=1,alpha=0.1) + 
        stat_smooth(se=FALSE,size=2) +
        stat_summary(fun.data="mean_quant", geom="ribbon", alpha=0.25) +
        geom_abline(colour = "black") +
        xlab(paste0(xlabtype," (Bayes)")) +
        ylab(paste0(ptype," (Method)"))

    print(p +scale_y_continuous(limits=c(0,maxy)) +
          scale_x_continuous(limits=c(0,maxlfsr)) +
            scale_colour_manual(values=cbbPalette,breaks=breaks,labels=labels))         
  }

```{r}
#plots estimated lfdr and lfsr against truth.
#ptype indicates whether to use lfsr or lfsra
#maxx controls maximum x axis value
#maxy controls maximum y axis value
plot_lfsdr=function(sims,maxx=0.1,ptype=c("lfsr","lfsra"),maxy=1){
    ptype=match.arg(ptype)
    res=list()
    res.lfsr=list()
    res.lfdr=list()

    for(i in 1:length(sims)){
      lfsr.ash.true= unlist(lapply(sims[[i]]$betahat.ash.true,"[[","lfsr"))
      lfsr.ash.n= unlist(lapply(sims[[i]]$betahat.ash.n,"[[",ptype))
      lfsr.ash.u= unlist(lapply(sims[[i]]$betahat.ash.u,"[[",ptype))

      lfdr.ash.n= unlist(lapply(sims[[i]]$betahat.ash.n,"[[","lfdr"))
      lfdr.ash.u= unlist(lapply(sims[[i]]$betahat.ash.u,"[[","lfdr"))
      lfdr.ash.true= unlist(lapply(sims[[i]]$betahat.ash.true,"[[","lfdr"))
      lfdr.mixfdr = unlist(lapply(sims[[i]]$betahat.mixfdr,"[[","fdr"))
      lfdr.locfdr = unlist(lapply(sims[[i]]$betahat.locfdr,"[[","fdr"))

      subset = lfsr.ash.true<maxx

      res.lfsr[[i]] = data.frame(Scenario=i,Measure='lfsr', ash.nullbiased=lfsr.ash.n[subset], ash.uniform=lfsr.ash.u[subset],Bayes=0.1*maxx*findInterval(lfsr.ash.true[subset],seq(0,maxx,length=11))-0.05*maxx,mixfdr = NA)

      subset = lfdr.ash.true<maxx
      res.lfdr[[i]] = data.frame(Scenario=i,Measure='lfdr', ash.nullbiased=lfdr.ash.n[subset], ash.uniform=lfdr.ash.u[subset],Bayes=0.1*maxx*findInterval(lfdr.ash.true[subset],seq(0,maxx,length=11))-0.05*maxx,mixfdr = lfdr.mixfdr[subset])

      res[[i]]=rbind(res.lfdr[[i]],res.lfsr[[i]])
    }

    require(reshape2)

    res.melt = melt(res, id.vars=c("Bayes","Scenario","Measure"),variable.name="Method")

    cbbPalette <- c("#000000","#E69F00", "#56B4E9", "#009E73", "#F0E442", "#0072B2", "#D55E00", "#CC79A7")
    labels = c('mixfdr','ash (null-biased)','ash (uniform)')
    breaks = c("mixfdr","ash.nullbiased","ash.uniform")

    p=ggplot(data=res.melt,aes(Bayes,value,colour=Method)) + 
        facet_grid(Measure ~ Scenario ) +
        #scale_fill_manual(values=cbbPalette) +
        #scale_colour_manual(values=cbbPalette) +
        geom_point(size=1,alpha=0.1) + 
        #stat_smooth(se=FALSE,size=2) +
        stat_summary(fun.data="mean_quant", geom="ribbon", alpha=0.25) +
        geom_abline(colour = "red",size=1) +
        xlab("Truth") +
        ylab("Estimate")

    print(p +scale_y_continuous(limits=c(0,maxy)) +
          scale_x_continuous(limits=c(0,maxx)) +
            scale_colour_manual(values=cbbPalette,breaks=breaks,labels=labels))        
  }

```{r}
png("figures/lfsdr_sim1sim2_blowup.png",height=427,width=720)
  plot_lfsdr(list(simres1,simres1a,simres2),0.1,ptype="lfsra")
dev.off()
```

```{r}
png("figures/lfdr_sim1sim2_blowup.png",height=160,width=540)
  plot_lfsr(list(simres1,simres1a,simres2),0.1,ptype="lfdr")
dev.off()
```

```{r}
png("figures/lfsra_sim1sim2_blowup.png",height=160,width=540)
  plot_lfsr(list(simres1,simres1a,simres2),0.1,ptype="lfsra")
dev.off()
```

```{r}
png("figures/lfsra_sim1sim2_blowup.png",height=160,width=540)
  plot_lfsr(list(simres1,simres1a,simres2),0.1,ptype="lfsr")
dev.off()
```

```{r}
    plot_pi0(simres3)
  plot_pi1(simres3)
```

@@

```{r}
#hh.ashtrue = hh.ashz
#hh.ashtrue$fitted.g$pi = c(2/3,1/15,1/15,1/15,1/15,1/15)
#hh.ashtrue$fitted.g$mean = c(0,0,0,0,0,0)
#hh.ashtrue$fitted.g$sd = sqrt(c(0,1,0.2,0.4,0.8,3))

#loglik(hh.ashtrue,betahat,sebetahat)
#loglik(hh.ashz,betahat,sebetahat)
```

### 2013-11-12 paper/main.tex
update ggplot2 figures

% Title must be 150 characters or less
\begin{flushleft}
{\Large
\textbf{Shrinkage, False Discovery Rate Estimation, and an alternative to the ``Zero assumption" when precision varies across units}
}
% Insert Author names, affiliations and corresponding author email.
\\
Matthew Stephens$^{1*}$, 
\\
\bf{1} Department of Statistics and Department of Human Genetics, University of Chicago, Chicago, IL, USA
\\
$\ast$ E-mail: Corresponding mstephens@uchicago.edu
\end{flushleft}

@@

A common goal, particularly in genomic studies, is to identify which $\beta_j$ differ from zero. This is commonly tackled
by first computing a $p$ value for each $j$, testing $H_j:\beta_j=0$, and then applying methods based on False Discovery Rates, such as the qvalue package. For example, we could compute $Z$ scores $Z_j = \beta_j/s_j$, and translate $Z_j$ to a $p$ value, 
$p_j$, and then use now-standard methods to select a $p$ value threshold to control the FDR.

@@

Following these ideas of \cite{gelman.etal}, we define the local False Sign Rate (lfsr) for observation $j$ as 
\begin{equation}
\lfsr_j := \min[ p(\beta_j \geq 0| \hat\beta, s), p(\beta_j \leq 0| \hat\beta, s) ].
\end{equation}
Thus $\lfsr_j$ gives the probability that we would get the sign of $\beta_j$ wrong if we
were to make our best guess. (Note that we count it as an error to state that $\beta$ is positive or negative when it is truly zero.)
To illustrate, suppose for concreteness
that the minimum is achieved by the first term, $p(\beta_j \geq 0| \hat\beta, s)=0.05$ say. Then
our best guess would be that $\beta$ is negative, and the probability that we have
made an error in sign would be 0.05.

@@

- Illustration that 2 local false sign rate is approximately local fdr.

@@

- Illustration of the difference between the zero assumption and no zero assumption on FDR
in case z is N(0,2) vs N(0,1). [no difference in precision]

>>>>

% Title must be 150 characters or less
\begin{flushleft}
{\Large
\textbf{Shrinkage, False Discovery Rate, and False Sign Rate Estimation when precision varies across units}
}
% Insert Author names, affiliations and corresponding author email.
\\
Matthew Stephens$^{1*}$, 
\\
\bf{1} Department of Statistics and Department of Human Genetics, University of Chicago, Chicago, IL, USA
\\
$\ast$ E-mail: Corresponding mstephens@uchicago.edu
\end{flushleft}

@@

A common goal, particularly in genomic studies, is to identify which $\beta_j$ differ from zero. This is commonly tackled
by first computing an effect size estimate ($\hat\beta_j$) and its standard error ($s_j$), converting this to a $Z$ score ($Z_j=\hat\beta_j/s_j$)
and a corresponding $p$ value ($p_j$), testing $H_j:\beta_j=0$.  Then standard methods (e.g. the qvalue package) can be used
to estimate False Discovery Rates at any given threshold.

@@

Following these ideas, we define the local False Sign Rate (lfsr) for observation $j$ as 
\begin{equation}
\lfsr_j := \min[ p(\beta_j \geq 0| \hat\beta, s), p(\beta_j \leq 0| \hat\beta, s) ].
\end{equation}
Thus $\lfsr_j$ gives the probability that we would get the sign of $\beta_j$ wrong if we
were to make our best guess. (Note that we count it as an error to state that $\beta$ is positive or negative when it is truly zero.)
To illustrate, suppose for concreteness
that the minimum is achieved by the first term, $p(\beta_j \geq 0| \hat\beta, s)=0.05$ say. Then
our best guess would be that $\beta$ is negative, and the probability that we have
made an error in sign would be 0.05. We note that the idea of focussing on tail areas, rather than point null hypotheses,
has a long history (e.g. Altham? others?).

@@

\subsection{Improved conservative estimation of $\pi_0$}

To illustrate, we provide simulation results for two scenarios, the first being a ``difficult" case where many non-zero $\beta$ are
too close to  zero to be reliably detected, and the second being an ``easier" case where most non-zero $\beta$ are
sufficiently different from zero that they can be reliably detected.

Specifically we use the following distributions for the non-zero $\beta$:
\begin{itemize}
\item[Simulation 1:]
\begin{equation}
f_1(\cdot) =  0.4 N(0,0.25^2) + 0.2 N(0,0.5^2) + 0.2 N(0,1^2), 0.2 N(0,2^2)
\end{equation}
\item[Simulation 2:]
\begin{equation}
f_1(\cdot) = N(0,4^2)
\end{equation}
\end{itemize}

Emphasize that although pi0 is unidentifiable, the underlying distribution g is estimable
quite accurately.

\subsection{Local False Sign Rate}

There are two reasons to use the lfsr instead of the lfdr: it is more generally meaningful (e.g. it applies
whether or not zero effects exist),  and estimation of lfsr is more robust to modeling assumptions.

\begin{figure}[!ht]
\begin{center}
\includegraphics[height=320px,width=540px]{Rcode/figures/lfsdr_sim1sim2_blowup.png}
\end{center}
\caption{Figure showing lfsr is more robust than lfdr}
\end{figure}

- Illustration that estimated lfsr is more robust.

- Illustration that adjusted estimate of lfsr is still more robust..

- Compare estimated lfsr with true lfsr for difficult simulation case, to show nearly achieves Bayes Risk?

\subsection{Accounting for measurement precision improves estimates of FDR/fsr}

@@
